Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-22 ICML-submission/introduction.tex
Fixes

\begin{protocol}[h]
\caption{\textsc{Online Multiclass Linear Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\textbf{Require:} Number of classes $K$, number of rounds $T$.\\
\For{$t=1,2,\dots,T$}{
Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.\\
Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
Observe feedback $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
}
\end{protocol}

>>>>

\begin{protocol}[h]
\caption{\textsc{Online Multiclass Linear Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\textbf{Require:} Number of classes $K$, number of rounds $T$. \\
\textbf{Require:} Inner product space $(V,\ip{\cdot}{\cdot})$. \\
\For{$t=1,2,\dots,T$}{
Adversary chooses example $(x_t, y_t) \in V \times \{1,2,\dots,K\}$ where $x_t$ is revealed to the learner.\\
Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
Observe feedback $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
}
\end{protocol}
